### 2016-09-28 syntax.tex
cheers
cleaning notation and syntax

When~$\univ$ is a set, we write $x \getsr \univ$ to denote sampling
an element uniformly from~$\univ$ and assigning it to~$x$. We extend
this notation to randomized algorithms, so $x \getsr A(y)$ denotes
that (randomized) algorithm $A$ is run on input~$y$, and the output
of the algorithm is assigned to~$x$. Algorithms may be provided
black-box access to one or more oracles, which we write as
superscripts, e.g., $F^{O_1,O_2,\ldots}$.

@@

%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix sets~${\cal U}, \Gamma$, and $\calQ = \{\qry \colon {\cal U} \to
\Gamma\}$. A \emph{data structure} (supporting queries $\calQ$ over
universe ${\cal U}$) is a tuple $\setprim=(\Rep, \Qry)$ where:
\begin{itemize}
\item $\Rep \colon {\cal U} \to \bits^* \times \bits^*$ is a
    randomized \emph{representation algorithm}, taking as input
    an element $S \in \mathcal{U}$,
    and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$.
    We write $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand
    for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $\qry \in \calQ$, and outputting an
    \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,\qry)$ for this execution. \hfill\dqed
\end{itemize}
\end{definition}

@@

\tsnote{Do we ever use this definition?  I guess it is a mapping of
  classical notions to our syntax, but I don't know if we use it.
  Anyway,  it looks a bit weird sitting here on its own.  It made more
  sense when supported by the intuition-building example, now
  commented out. }
\begin{definition}[Error probability and rate] \rm
For a specific data structure $\setprim=(\Rep, \Qry)$ supporting
queries ${\cal Q}$ over universe ${\cal U}$, let
$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we say that $\Pi$
has \emph{error probability}~$\epsilon$ if
\[\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon.\]
%
We say it has \emph{error rate} $\tilde{\epsilon}$ if
\[{\textstyle \max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1]} \leq \tilde{\epsilon}. \]
%\hfill\dqed
\end{definition}

@@

\heading{Data structures for set-membership queries.} An important
special case is a data structure that supports set-membership
queries. \jnote{I changed this from multiplicity to membership.}

\begin{definition} \rm
A \emph{set-membership data structure over $\univ$} is a data
structure with ${\cal U} \subseteq 2^\univ$, $\Gamma=\{0,1\}$, and
$\calQ=\{\qry_x\}_{x \in \univ}$, where $\qry_x(S)$ is true iff $x
\in S$. \hfill\dqed
\end{definition}

Note that we do not require ${\cal U} = 2^\univ$ since, e.g., a
set-membership data structure may only be defined for sets up to
some bounded size.

>>>>

When~$\univ$ is a set, we write $x \getsr \univ$ to denote sampling
an element uniformly from~$\univ$ and assigning it to~$x$. We extend
this notation to randomized algorithms, so $x \getsr A(y)$ denotes
that (randomized) algorithm $A$ is run on input~$y$, and the output
of the algorithm is assigned to~$x$. Algorithms may be provided
black-box access to one or more oracles, which we write as
superscripts, e.g., $F^{O_1,O_2,\ldots}$.  We write $\langle
x,y,\ldots \rangle$ for the encoding of values $x,y,\ldots$ as a
single bitstring, for some implicit and invertible encoding method.
When $x$ is a string, we write $x[i]$ for the $i$-th element in that string.

@@

%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix sets~$\univ, \Gamma$, and $\calQ = \{\qry \colon \univ \to
\Gamma\}$. A \emph{data structure} (supporting queries $\calQ$ over
universe $\univ$) is a tuple $\setprim=(\Rep, \Qry)$ where:
\begin{itemize}
\item $\Rep \colon \univ \to \bits^* \times \bits^*$ is a
    randomized \emph{representation algorithm}, taking as input
    an element $S \in \univ$,
    and outputting %a \emph{representation} $M \in \Sigma^*$,
    \emph{public representation data} $\pubaux \in \bits^*$ and
    \emph{private representation data} $\privaux \in \bits^*$.
    We write $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand
    for this execution.
\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
    and a query $\qry \in \calQ$, and outputting an
    \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(\pubaux,\privaux,\qry)$ for this execution. \hfill\dqed
\end{itemize}
\end{definition}

@@

\tsnote{Do we ever use this definition?  I guess it is a mapping of
  classical notions to our syntax, but I don't know if we use it.
  Anyway,  it looks a bit weird sitting here on its own.  It made more
  sense when supported by the intuition-building example, now
  commented out. }
\begin{definition}[Error probability and rate] \rm
For a specific data structure $\setprim=(\Rep, \Qry)$ supporting
queries $\calQ$ over universe $\univ$, let
$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we say that $\Pi$
has \emph{error probability}~$\epsilon$ if
\[\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon.\]
%
We say it has \emph{error rate} $\tilde{\epsilon}$ if
\[{\textstyle \max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
\mathrm{Err}(S,\qry,\pubaux,\privaux)=1]} \leq \tilde{\epsilon}. \]
%\hfill\dqed
\end{definition}

@@

%\heading{Data structures for set-membership queries.} 
An important special case is a data structure that supports set-membership
queries. \jnote{I changed this from multiplicity to membership.}

\begin{definition} \rm
A \emph{set-membership data structure over $\univ$} is a data
structure with $\univ \subseteq 2^\elts$, $\Gamma=\{0,1\}$, and
$\calQ=\{\qry_x\}_{x \in \univ}$, where $\qry_x(S)$ is true iff $x
\in S$. \hfill\dqed
\end{definition}

Note that we do not require $\univ = 2^\elts$ since, e.g., a
set-membership data structure may only be defined for sets up to
some bounded size.
